Neonatal models

### 2021-12-01 neo.Rmd
look for errors (found but not fixed)

```{r readdata}
infdat <- readRDS("data/infdat.rds")[, c("id", "enter", "exit", "event", 
                                         "sex", "socStatus", "illeg",  
                                         "parity", "cold", "week")]
## remove zero-length spells:
infdat <- infdat[infdat$exit > infdat$enter + 1.e-6, ] 
rownames(infdat) <- 1:NROW(infdat)
NROW(infdat)
length(unique(infdat$id))
head(infdat)
```

@@

```{r agecut}
library(eha)
neo <- age.window(infdat, c(0, 28 / 365))
```

@@

```{r transform}
neo$enter <- round(365 * neo$enter)
neo$exit <- round(365 * neo$exit)
neo <- neo[neo$exit > neo$enter, ] # Remove zero-length spells

dim(neo)
head(neo)
```

@@

```{r clean}
neo <- neo[neo$parity > 0, ] # Remove missing = -1
neo$parity <- cut(neo$parity, c(0, 1.5, 3.5, 18.5), labels = c("1", "2-3", "4+"))
neo <- neo[!is.na(neo$socStatus), ] # Remove records with missing values
```

>>>>

```{r readdata}
infdat <- readRDS("data/infdat.rds")[, c("id", "enter", "exit", "event", 
                                         "sex", "socStatus", "illeg",  
                                         "parity", "cold", "week")]
## remove zero-length spells:
infdat <- infdat[infdat$exit > infdat$enter + 1.e-6, ] 
rownames(infdat) <- 1:NROW(infdat)
NROW(infdat)
length(unique(infdat$id))
head(infdat) ## OK!
```

@@

```{r agecut}
library(eha)
neo <- age.window(infdat, c(0, 28 / 365))
## events = 2693
```

@@

```{r transform}
##neo$enter <- round(365 * neo$enter)
##neo$exit <- round(365 * neo$exit)
##neo <- neo[neo$exit > neo$enter, ] # Remove zero-length spells
neo$enter <- 365 * neo$enter
neo$exit <- 365 * neo$exit
dim(neo)
head(neo) ## OK
```

@@

```{r clean}
neo <- neo[neo$parity > 0, ] # Remove missing = -1
neo$parity <- cut(neo$parity, c(0, 1.5, 3.5, 18.5), labels = c("1", "2-3", "4+"))
##neo <- neo[!is.na(neo$socStatus), ] # Remove records with missing values
## Instead, replace missing socStatus with "low"
neo$socStatus[is.na(neo$socStatus)] <- "low"
```
